---
title: "Demonstration of slide lay out"
author: "The Authors"
subtitle: "The optional subtitle"
usepackage: "lipsum"

output: 
  corpident::ci_slides_pdf:
    location: "Location and date"
    institute: "Affiliation of the author"
    slide_level: 3

  corpident::ci_handouts_pdf:
    location: "Location and date"
    institute: "Affiliation of the author"
    slide_level: 3
    keep_tex: FALSE
    
  corpident::ci_report_pdf:
    cover: "Frog"
    cover_text: "Frog Macro Portrait by Karen Arnold. CC0. (\\url{http://www.publicdomainpictures.net/browse-author.php?a=32495})"
    cover_offset: "135mm"
---

```{r setup, echo=FALSE, results='hide'}
library(pander)
```


# Text a b c d e f g h i j k l m n o p q r s t u v w x y z 0 1 2 3 4 5 6 7 8 9 a b c d e f g h i j k l m n o p q r s t u

## Fonts

### Plain font

\lipsum[1] 

### Monospace font
  
\texttt{\lipsum[2-3]}

### Bold font
  
**\lipsum[4-6]**

### Italics font

_\lipsum[7-9]}_

### Accents and stuff
  
äàáâã ëèéê ïìíî öòóô üùúû ÿ ç ñ 
  
ÄÀÁÂ ËÈÉÊ ÏÌÍÎ ÖÒÓÔ ÜÙÚÛ Ñ
  
"double quotes"

'single quotes'

uppercase i versus lowercase L: Il



















## Lists a b c d e f g h i j k l m n o p q r s t u v w x y z 0 1 2 3 4 5 6 7 8 9 a b c d e f g h i j k l m n o p q r s t u v w x y

### Itemize with 3 levels with some extra nonsens in a very long title so that the title will be longer than a single line.

- first item
- second item
    - first item
        - first item
        - second item
        - third item
        - forth item
    - second item
    - third item
    - forth item
- third item
- forth item

### Enumerate

1. first item
1. second item
    9. first item
    1. second item
    1. third item
        1. first item
        1. second item
        1. third item
        1. forth item
    1. forth item
1. third item
1. forth item

### Description

First
  ~ Description of the first item
  
    Version A
      ~ Details of A
      
    Version B
      ~ Details of B
Second
  ~ Description of the second item






















## Different kinds of blocks

### Block

#### The title of the block

\lipsum[10-12]

### Exampleblock
  
\begin{exampleblock}{The title of an example block}
  \lipsum[13-14]
\end{exampleblock}

### Alertblock

\begin{alertblock}{The title of an alert block}
\lipsum[15-16]
\end{alertblock}

## Other stuff

### Equations

Inline $f(x | \mu, \sigma) = \frac{1}{\sigma\sqrt{2\pi}}\, e^{-\frac{(x - \mu)^2}{2 \sigma^2}}$


$$f(x | \mu, \sigma) = \frac{1}{\sigma\sqrt{2\pi}}\, e^{-\frac{(x - \mu)^2}{2 \sigma^2}}$$












# R Code

## Examples

### Code

```{r prepare_graphics}
library(knitr)
opts_chunk$set(
  inline = TRUE,
  strip.white = FALSE,
  message = FALSE,
  warning = FALSE
)
library(ggplot2)
theme_set(theme_gray(6))
```

### Datasets

```{r datasets}
example <- data.frame(
  Day = c("Monday", "Tuesday", "Wednesday"),
  'Min Temp' = c("11C", "9C", "10C"),
  'Max Temp' = c("22C", "19C", "21C"),
  Summary = c(
    "A clear day with lots of sunshine. However, the 
    strong breeze will bring down the temperatures.", 
    "Cloudy with rain, across many northern regions. 
    Clear spells across most of Scotland and Northern 
    Ireland, but rain reaching the far northwest.", 
    "Rain will still linger for the morning. Conditions 
    will improve by early afternoon and continue 
    throughout the evening."
  )
)
str(example)
```

# Tables and figures

## Tables

### Multiline table

```{r multiline_table, results='asis'}
pandoc.table(example)
```

### Grid table

```{r grid_table, results='asis'}
pandoc.table(example, style = "grid")
```

## Figures

### Figures {.allowframebreaks}

```{r figstandard, out.extra = ''}
ggplot(movies, aes(x = rating)) + 
  geom_histogram() + 
  facet_wrap(~ mpaa, scales = "free")
ggplot(diamonds, aes(x = price, fill = cut)) + 
  geom_histogram()
ggplot(
  mtcars, 
  aes(
    x = wt, 
    y = mpg, 
    colour = factor(cyl), 
    fill = factor(cyl)
  )
) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

